Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-03-28 Documents/M1/realizableFermionicM1/sections/realizability.tex
Split section 3 in two: Moment Realizability... and Algebraic Moment Closures

\section{Moment Realizability and Algebraic Closures for the Fermionic Two-Moment Model}
\label{sec:realizability}

@@

\subsection{Moment Realizability}

@@

\begin{lemma}
  Let $\vect{\cM}_{a}$ and $\alpha$ be given as in Lemma~\ref{lem:implicitStep}, and let $\vect{\cM}_{b}$ satisfy
  \begin{equation*}
    \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{b}),    
  \end{equation*}
  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments}.  
  Then $\vect{\cM}_{b}\in\cR$.  
  \label{lem:correctionStep}
\end{lemma}

\begin{proof}
  The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep}.  
\end{proof}

\subsection{Algebraic Moment Closures}

Algebraic moment closures for the two-moment model are computationally efficient as they provide the Eddington factor in Eq.~\eqref{eq:eddingtonTensor} in closed form as a function of the density $\cJ$ and the flux factor $h=|\vect{\cH}|/\cJ$.  
The family of algebraic closures we consider in this paper can be written in the form \cite{cernohorskyBludman_1994}
\begin{equation}
  \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big),
\end{equation}
where the closure function $\Theta(x)$ varies with the specifics of the closure procedure.  
We will consider two basic closure procedures in more detail below: the maximum entropy (ME) closure and the Kershaw (K) closure.

\subsubsection{Maximum Entropy Closure}
The basic principle behind the maximum entropy closure is that one can approximate the real fermion distribution with a distribution which having the Fermi-Dirac distribution form 
\begin{equation}
f(\omega)=\f{1}{e^{a + b\omega}+1}, 
\end{equation} 
meanwhile, maximizing the entropy function
\begin{equation}
S[f(\omega)] = (1-f)\log(1-f) + f\log f.
\end{equation} 
Given moments $\cJ$ and $\vect{\cH}$, a distribution satisfying above requirements can be found. Hence, $\vect{\cK}$.

Chernohorsky \& Bludman \cite{cernohorskyBludman_1994}
\begin{equation}
  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}(x)
  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big)
\end{equation}

Banach \& Larecki \cite{banachLarecki_2017b}
\begin{equation}
  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}(x)
  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big)
\end{equation}

\subsubsection{Kershaw Closure}
The basic principles behind Kershaw closure is that since $\cR$ is convex and bounded, every element in $\cR$ can be written as a convex combination of the elements on the realization boundary.
For fermionic radiation, the boundary is based on the Heaviside step functions.

Banach \& Larecki \cite{banachLarecki_2017a}
\begin{equation}
  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
\end{equation}

\subsubsection{Low Occupancy Limit}

Figure~\ref{fig:MabWithDifferentClosure} illustrates the behavior of these four closure.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLME}
    \includegraphics[width=0.5\textwidth]{figures/MabWithCBME} \\
    \includegraphics[width=0.5\textwidth]{figures/MabWithBLKS}
    \includegraphics[width=0.5\textwidth]{figures/MabWithMI}
  \end{tabular}
   \caption{Illustration of $\vect{\cM}_{ab}$ with four different closures: Banach \& Larecki maximum entropy closure (left top), Chernohorsky \& Bludman maximum entropy closure (right top), Kershaw closure (left bottom), and Minerbo closure (right bottom).
   Total $10^{6}$ pairs of random Fermi-Dirac distribution were generated.
   With these pairs, $\vect{\cM}_{ab}$ with different closures were calculated separately and marked with light-blue points.
   Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
  \label{fig:MabWithDifferentClosure}
\end{figure}

>>>>

\section{Moment Realizability for the Fermionic Two-Moment Model}
\label{sec:realizability}

@@

@@

\begin{lemma}
  Let $\vect{\cM}_{a}$ and $\alpha$ be given as in Lemma~\ref{lem:implicitStep}, and let $\vect{\cM}_{b}$ satisfy
  \begin{equation*}
    \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{b}),    
  \end{equation*}
  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments},  then $\vect{\cM}_{b}\in\cR$.  
  \label{lem:correctionStep}
\end{lemma}
The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep} and is omitted.
